K8S RESOURCE\\ SHARING

### 2019-10-02 openinfranordics2019/presentation.tex
Improve schedulers diagram

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{center}
        \begin{tikzpicture}[
            queue/.style={line width=0.5mm},
            connection/.style={-,>=stealth',semithick,rounded corners=5pt}
            ]
            \draw[fill=gray!20, rounded corners] (0, 0) rectangle (12, 8) node[pos=0.5] {};
            \draw[fill=gray!40, rounded corners] (0.2, 0.2) rectangle (5.8, 7.8) node[pos=0.5, text depth=6cm] {I/O sched};
            \draw[fill=gray!40, text depth=6cm] (6.2, 0.2) rectangle (11.8, 7.8) node[pos=0.5] {blkmq};

@@

>>>>

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{center}
        \begin{overprint}

        \onslide<1>
        \begin{tikzpicture}[
            queue/.style={line width=0.5mm},
            connection/.style={-,>=stealth',semithick,rounded corners=5pt}
            ]
            \draw[fill=gray!20, rounded corners] (0, 0) rectangle (12, 8) node[pos=0.5] {};
            \draw[fill=gray!40, rounded corners] (0.2, 0.2) rectangle (5.8, 7.8) node[pos=0.5, text depth=6cm] {I/O sched};
            \draw[fill=gray!40, text depth=6cm] (6.2, 0.2) rectangle (11.8, 7.8) node[pos=0.5] {blkmq};

@@

        \onslide<2>
        \begin{tikzpicture}[
            queue/.style={line width=0.5mm},
            connection/.style={-,>=stealth',semithick,rounded corners=5pt}
            ]
            \draw[fill=gray!20, rounded corners] (0, 0) rectangle (12, 8) node[pos=0.5] {};
            \draw[fill=gray!40, rounded corners] (0.2, 0.2) rectangle (5.8, 7.8) node[pos=0.5, text depth=6cm] {I/O sched};
            \draw[fill=gray!40, text depth=6cm] (6.2, 0.2) rectangle (11.8, 7.8) node[pos=0.5] {blkmq};

            \draw[fill=yellow!60, rounded corners] (0.4 + 6, 5.3) rectangle (2.2 + 6, 6.0) node[pos=0.5] (none) {\normalsize{\textbf{none}}};
            \coordinate[above=0.5 of none] (none-arrow);
            \draw[
                fill=red!20,
                dashed,
                rounded corners,
                line width=0.2mm
            ]
            (2.4 + 6 - 0.1, 5.3 - 0.1) rectangle (4.4 + 6 + 0.1, 6.0 + 0.1)
            node[pos=0.5] {};
            \draw[fill=yellow!60, rounded corners] (2.4 + 6, 5.3) rectangle (4.4 + 6, 6.0) node[pos=0.5] (kyber) {\normalsize{\textbf{kyber}}};
            \coordinate[above=0.5 of kyber] (kyber-arrow);
            \draw[fill=yellow!60, rounded corners] (4.6 + 6, 5.3) rectangle (5.4 + 6, 6.0) node[pos=0.5] (others)  {\normalsize{\textbf{...}}};
            \coordinate[above=0.5 of others] (others-arrow);

            \draw[queue, fill=black!50] (9.0 - 0.5, 0.4) rectangle (9.5 - 0.5, 0.8) node[pos=0.5] {};
            \draw[queue, fill=black!50] (9.0 - 0.5, 0.8) rectangle (9.5 - 0.5, 1.2) node[pos=0.5] {};
            \draw[queue] (9.0 - 0.5, 1.2) rectangle (9.5 - 0.5, 1.6) node[pos=0.5] {};
            \draw[queue] (9.0 - 0.5, 1.6) rectangle (9.5 - 0.5, 2.0) node[pos=0.5] (hw-queue-1) {};

            \draw [thick,decorate,decoration={brace,amplitude=5pt}]
                (9.75, 2.0 + 2.5)  -- (9.75, 0.4 + 2.5)
                node[black, midway, right=4pt, font=\normalsize, text width=3cm] {Software\\queue};
        \end{tikzpicture}
    \end{overprint}
